### 2018-03-10 paper/build.tex
More todos

\begin{quote}
A build system must build \underline{out-of-date targets} while \underline{respecting dependency orderings}.
\end{quote}

\todo{NM}{We haven't used the term `target' before, perhaps change to `keys'?}

>>>>

\begin{quote}
A build system must build \underline{out-of-date keys} while \underline{respecting dependency orderings}.
\end{quote}
